Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-08 main.tex
Add FSM diagrams to text.

Training this strategy corresponds to finding mappings of states and histories
to an action and a state. Figures~\ref{} show two of the trained finite state
machines...
% TODO Update sentence above.
% TODO Add diagrams of FSMs. Note how the strategies are called FSM 16 but as is
% evident in the diagram, it is in fact a 14 state fsm.

>>>>

Training this strategy corresponds to finding mappings of states and histories
to an action and a state. Figure~\ref{fig:fsm_images} show two of the trained
finite state machines. The layout of state nodes is kept the same between
Figure~\ref{fig:fsm16} and~\ref{fig:fsm16noise} to highlight the effect of
different training environments. Note also that two of the 16 states are not
used, this is also an outcome of the training process.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \includestandalone[height=.3\textheight]{./assets/FSM16}
        \caption{Evolved\_FSM\_16: trained to maximise score in a standard
        tournament}
        \label{fig:fsm16}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includestandalone[height=.3\textheight]{./assets/FSM16noise}
        \caption{Evolved\_FSM\_16\_Noise\_05: trained to maximise score in a
        noisy tournament}
        \label{fig:fsm16noise}
    \end{subfigure}%
    \caption{Trained sixteen state finite state machine players}
    \label{fig:fsm_images}
\end{figure}
